Automated verification of stand-alone solar photovoltaic systems

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@

We performed five case studies: (a) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (b) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h). The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}). Another characteristic of Manaus, based on historic data of solar irradiance, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
\subsection{Results}
\label{sec:results_indeed}
The total were five case studies evaluated by HOMER Pro and by the automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by four systems, without any indication of sizing error or even of performance. The case study that was not successful during simulation was the 1,200 W (house 5), however without indication what are the fail of this PV system. All the simulations took less than 5 seconds (each) to be performed.

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------
%The proposed tool seems to be a coherent and promising tool to perform verification of a PV project. The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field. 
%
%The automated verification tool presented here establishes the automated verification and the project sizing check. 
It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results. The proposed tool was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems. That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system. 
Next, the proposed tool will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs. This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.

Furthermore, it is possible to contemplate other kinds of renewable energy and even hybrid ones, which can evolve the algorithm into a complete tool for design and verification for rural electrification.
% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

>>>>

%------------------------------------------

@@

We performed five case studies: (a) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (b) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h). The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}). Another characteristic of Manaus, based on historic data of solar irradiance, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------

The total were five case studies evaluated by HOMER Pro and by the automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by four systems, without any indication of sizing error or even of performance. The case study that was not successful during simulation was the 1,200 W (house 5), however without indication what are the fail of this PV system. All the simulations took less than 5 seconds (each) to be performed.

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------

We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions, in terms of temperature and solar irradiation, a PV system can fail. As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems. We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.

% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.
